% chmduquesne.tex - Auto-generated ConTeXt Resume
\starttext

% Set up fonts and colors
\definefontfamily[mainface][rm][Arial]
\setupbodyfont[mainface,11pt]
\definecolor[sectionblue][c=0.8,m=0.5,y=0,k=0]
\definecolor[nameblue][c=0.8,m=0.5,y=0,k=0]

% Name and Title
\startalignment[middle]
{\tfd\bf\color[nameblue]{Alex Carter}}\\
{\tfa Senior Full Stack Developer (Laravel)}
\stopalignment

% Contact Information
\startalignment[right]
\starttabulate[|l|l|]
\NC Email: \NC alex.carter@example.com \NC\NR
\NC Phone: \NC +1 555 123 4567 \NC\NR
\NC Location: \NC Toronto, Canada \NC\NR
\NC LinkedIn: \NC \goto{alex-carter}[url(https://www.linkedin.com/in/alex-carter)] \NC\NR
\NC GitHub: \NC \goto{alexcdev}[url(https://github.com/alexcdev)] \NC\NR
\stoptabulate
\stopalignment

% Summary
\blank[medium]
{\tfa\bf\color[sectionblue]{SUMMARY}}
\blank[small]
Creative and detail-oriented full-stack developer with 6+ years of experience designing scalable web applications. Expert in Laravel, PHP, MySQL, Vue.js, and Docker. Proven track record in optimizing, refactoring, and scaling platforms. Passionate about clean code, thoughtful UX, and continuous learning. Experienced in both startup and enterprise environments. Strong analytical mindset and attention to detail.

% Professional Experience
\blank[medium]
{\tfa\bf\color[sectionblue]{PROFESSIONAL EXPERIENCE}}
\blank[small]
\startitemize[packed]
\item {\bf SignalStack (Remote, Europe)} \hfill Dec 2024 -- Present\\
{\it Senior Full Stack Developer}
\startitemize[packed]
  \item Migrated frontend from AngularJS to Vue 3, modernizing the platform for scalability and maintainability.
  \item Dockerized development and CI/CD pipeline, improving deployment speed and reliability.
  \item Proposed and executed a frontend rebuild roadmap; helped hire and onboard new developers.
\stopitemize
\item {\bf ProjectNest (Remote, US-based SaaS)} \hfill Sep 2021 -- Dec 2024\\
{\it Full Stack Developer}
\startitemize[packed]
  \item Built and maintained core features using Laravel, Vue 3, Tailwind, and Docker.
  \item Integrated third-party tools (Stripe, Intercom, Segment, Zapier) to enhance platform capabilities.
  \item Designed and implemented a Development Panel for customer support operations.
  \item Refactored frontend to TypeScript; introduced dark mode and improved UX.
  \item Added PDF/CSV export, chart view, onboarding, and end-to-end tests (Cypress).
\stopitemize
\item {\bf Freelance Sports Platform (alexsports.dev)} \hfill May 2014 -- Present\\
{\it Founder / Lead Developer}
\startitemize[packed]
  \item Built and scaled a nationwide sports event platform serving 100k+ users.
  \item Designed architecture and developed frontend/backend with Laravel, Vue.js, MySQL.
  \item Integrated real-time syncing, Dockerized deployment, and automated testing.
  \item Maintained high system availability and performance over 10+ years.
\stopitemize
\item {\bf CyberSec Lab -- Horizon University} \hfill Jul 2016 -- Sep 2019\\
{\it Research Assistant}
\startitemize[packed]
  \item Conducted security audits and penetration testing using OWASP guidelines.
  \item Gave workshops on secure web development with Laravel.
  \item Built a single sign-on system for lab tools.
\stopitemize
\stopitemize

% Education
\blank[medium]
{\tfa\bf\color[sectionblue]{EDUCATION}}
\blank[small]
\startitemize[packed]
\item {\bf Tech University of Canada} \hfill 2019--2021\\
Master's in Bioinformatics, GPA: 3.6
\item {\bf Metro State University} \hfill 2013--2017\\
Bachelor's in Computer Engineering, GPA: 3.8, Graduated with Honors
\stopitemize

% Areas of Expertise
\blank[medium]
{\tfa\bf\color[sectionblue]{AREAS OF EXPERTISE}}
\blank[small]
\startcolumns[n=2]
\startitemize[packed]
  \item Laravel, PHP, MySQL
  \item Vue.js, JavaScript, TypeScript
  \item Docker, CI/CD, DevOps
  \item Cloud Solutions
  \item Secure Web Development
  \item API Integration
  \item Real-time Systems
  \item Automated Testing
  \item UX/UI Design
  \item Agile Methodologies
  \item Team Leadership
  \item Multilingual: English, Spanish, Japanese
\stopitemize
\stopcolumns

\stoptext
